\documentclass{easychair}
\titlerunning{SMT 2019}
\authorrunning{Preface}
\pagenumbering{roman}
\setcounter{page}{1}
\begin{document}

\section*{Preface}

This volume constitutes informal\ workshop proceedings and\ contains
the papers presented at SMT 2019: 17th International Workshop on
Satisfiability Modulo Theories held on July 7-8, 2019 in Lisbon.

The aim of the workshop is to bring together researchers and users of
SMT tools and techniques. The papers in this volume include both
original research papers as well as more extended abstracts and
preliminary reports of work in progress that may be of interest to the
SMT community. Each of these papers were reviewed by three
reviewers. In addition, this volume includes descriptions of each of
the\ tools participating in the 14th\ International Satisfiability
Modulo Theories Competition (SMT-COMP 2019).

Though not in this volume the SMT workshop included presentations
describing recent work published elsewhere of interest to the SMT
community. Each of these submissions were evaluated by three
reviewers. The presentation only papers include:




\begin{itemize}

\item Extending SMT solvers to Higher-Order Logic\\
  Haniel Barbosa, Andrew Reynolds, Daniel El Ouraoui, Cesare Tinelli and Clark
  Barrett

\item SPASS-SATT: a CDCL(LA) Solver\\
  Martin Bromberger, Mathias
  Fleury, Simon Schwarz and Christoph Weidenbach

\item Towards Bit-Width-Independent Proofs in SMT Solvers\\
  Aina Niemetz, Mathias Preiner, Andrew Reynolds, Yoni Zohar, Clark Barrett and Cesare Tinelli

\item High-Level Abstractions for Simplifying Extended String Constraints in SMT\\
  Andrew Reynolds, Andres Noetzli, Clark Barrett and Cesare Tinelli

\end{itemize}


We would like to thank the program committee and other reviewers for
their help in evaluating submissions. We would also like to thank the
organizers of the SMT competition\ Liana Hadarean,\ Antti
Hyvarinen,\ Aina Niemetz and\ Giles Reger for organizing the
competition with additional help from Mathias\ Preiner, Marco Gario
and\ Andres Noetzli.\ We would also like to thank the Nikolaj
Bj{\o}rner, Roberto Sebastiani, Clark Barrett, Pascal Fontaine, the
presenters at the workshop, and session chairs for their help in
making the event successful. \ We appreciate the EasyChair developers
in making in much easier to prepare volumes such as this and organize
workshops. \ Finally, we would like to thank the organizers of the SAT
conference and in particular, the workshop chair, Vasco Manquinho, for
help with local arrangements.


~\bigskip


\noindent
\begin{minipage}[t]{.4\textwidth}
June 26, 2019\\
Lugano, Switzerland\\
Portland, Oregon, United States
\end{minipage}%
\hfill
\begin{minipage}[t]{.4\textwidth}\flushright
\ \\
Natasha Sharygina\\
Joe Hendrix
\end{minipage}

\end{document}
